---
title: "Checking and tiding up the climate data"
author: "Junqi ZHU"
output:
  html_document: default
editor_options: 
  chunk_output_type: inline
---

```{r, warning=FALSE, echo=FALSE, tidy=TRUE, error=FALSE, message=FALSE}
 rm(list = ls())
    {
    library(plyr)
    l_ply(list('tidyverse','readxl','tidyr','dplyr','ggplot2','broom','ggthemes','plotly','purrr',
               'reshape2','cowplot','grid', 'reshape2','lubridate', 'RColorBrewer', 'datacheck'), 
          require, character.only = T)
    # tidyverse_update(recursive = FALSE) #updating packages
    #get the current working directory
    MainDir <- list(PROJHOME = normalizePath(getwd()))
    # Input and output directory data file location
    ExpData = file.path(MainDir, 'ExpData')
    # figure output directory, mainly the the place for paper writing 
    FigureOutput = file.path(MainDir, 'Figures')
    
    # Output directory, final results except figures, like statistics, and intermediate data set
    IntermediateResults = file.path(MainDir, 'Intermediate results')  
    SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # CustomizedFunctions = file.path('H:/Programming language/R language/Customized function library/')
    CustomizedFunctions = file.path(MainDir, 'customizedFunctionsLib')
    # Load all functions
    source(file.path(CustomizedFunctions,'Customized_curve_fitting_functions.R'))
    source(file.path(CustomizedFunctions,'Customized_functions_data_reconstruction.R'))
    source(file.path(CustomizedFunctions,'Customized_functions_for_photosynthesis.R'))
    
    source(file.path(SupportingFunctions,'Layout_of_ggplot.R'))
    source(file.path(SupportingFunctions,'Specific_functions.R'))
    # lsf.str()  #list of functions
    } 
```

# A remind of the subject that you are working on
```{r}
current.region <- 'Site1004_RPC'
current.subject <- 'Daily_New'

output.name <- paste(current.region, current.subject, sep = '_')
print(output.name)

```

## Load the data
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
library(openxlsx)

daily.data.24am.int <- 
  tbl_df(read_xlsx(file.path(ExpData, 'RPC New.xlsx'), 
                   sheet = 'RPC_Daily_12am', col_names = F)) 

 daily.data.24am <- 
  daily.data.24am.int %>% 
  slice(-c(1:5)) %>% 
  select(2:12,17:18) %>%
  setNames(gsub(" ",".",tolower(.[1,]))) %>%
  slice(-1) %>%
  mutate(time.max.air.temp = dmy_hm(time.max.air.temp), 
         time.min.air.temp = dmy_hm(time.min.air.temp), 
         tim.max.wind.speed = dmy_hm(tim.max.wind.speed)) %>% 
  # mutate(date = convertToDate(date, origin =  "1900-01-01")) %>% 
   mutate(date = date(dmy_hm(timestamp))) %>%
   mutate_if(is.character, funs( as.numeric(as.character(.)))) %>%
  mutate_if(is.numeric,funs(replace(.,is.na(.), mean(.,na.rm=TRUE)))) %>% 
  mutate(day = yday(date), hour = "24:00") %>% 
  select(stn.no. = siteid, year, day, date, 
         max.temp = max.air.temp,
         min.temp = min.air.temp,
         total.rain = rain_tot, 
         wind.m.s = mean.wind.speed) %>% 
  filter(year>= 2019) %>% 
  filter(!(year==2019 & day<=143))

glimpse(daily.data.24am)

short_summary(daily.data.24am)

```


## create a complete records of days
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
first.day <- first(daily.data.24am$day)
first.year <- first(daily.data.24am$year)
last.day <- last(daily.data.24am$day)
last.year <- last(daily.data.24am$year)

start.date <- as.Date(first.day, origin = paste(first.year-1, 12, 31, sep = '-'))
end.date <- as.Date(last.day, origin = paste(last.year-1, 12, 31, sep = '-'))

yday(end.date)

complete.year.day <- 
  data_frame(date = seq.Date(from = start.date,to = end.date, by = 'day')) %>% 
  mutate(year = year(date), day.of.year = yday(date))

glimpse(complete.year.day)
  
  
```
# Check the missing data and replace missing value
```{r, fig.width=15, fig.height=25,echo=FALSE}
# complete.daily.date <- 
right_join(daily.data.24am, complete.year.day, by = c('year','day' ='day.of.year')) %>% 
    # filter(is.na(min.temp))
filter(min.temp <= -15)
# filter(max.temp >= 40)

right_join(daily.data.24am, complete.year.day, by = c('year','day' ='day.of.year')) %>% 
  short_summary(.)
  
complete.daily.24am <- 
  right_join(daily.data.24am, complete.year.day, by = c('year','day' ='day.of.year', 'date')) %>% 
  group_by(day) %>% 
  mutate(min.temp = if_else(min.temp <= -15, as.double(NA), min.temp)) %>% 
  mutate_if(is.numeric,funs(replace(.,is.nan(.),NA))) %>% 
  mutate_at('total.rain',funs(replace(.,is.na(.),0))) %>% 
  mutate_at(vars(max.temp:wind.m.s),funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  ungroup(.) %>% 
  distinct(date, .keep_all = TRUE)

  # glimpse(complete.daily.24am)
short_summary(complete.daily.24am)



  
```

## combine with hourl calculated data
###relative humidity and sometimes radiation or wind speed is missing from the daily data
```{r, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# relative humidity data are mainly missing from the data
daily.hourl.cal <- 
  tbl_df(read_csv(file.path(IntermediateResults,                                          
                            'Site1004_RPC_Hourly_New.daily.cal.csv'))) %>% 
  select(-wind.m.s, -X1)
  

glimpse(daily.hourl.cal)

complete.daily.data <- 
  full_join(complete.daily.24am, daily.hourl.cal, by = c('year','day')) %>% 
  group_by(day) %>% 
  mutate_if(is.numeric,funs(replace(.,is.na(.), mean(.,na.rm=TRUE)))) %>% 
  mutate(vpd = VPD((max.temp +min.temp)/2, mean.rh/100)) %>% 
  select(stn.no.,year,day, max.temp, min.temp, total.rain, 
         wind.m.s, mean.rh, vpd)  
    
  
    
short_summary(complete.daily.data)  

```


# combine with blenheim radiation data
## add the missing radiation data from the blenheim data
```{r,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# relative humidity data are mainly missing from the data
blenheim.radiation <- 
  tbl_df(read.csv(file.path(IntermediateResults, 
                            'MRL_Daily_New.csv'), header = TRUE)) %>% 
  select(year, day, daily.solar.rad.mj.m2)
  

glimpse(blenheim.radiation)

complete.daily.data.radiation <-
  full_join(complete.daily.data, blenheim.radiation, by = c('year','day')) %>% 
  group_by(day) %>% 
  mutate_at('daily.solar.rad.mj.m2',funs(replace(.,is.na(.), mean(.,na.rm=TRUE)))) %>% 
  filter(!is.na(max.temp))


short_summary(complete.daily.data.radiation)  

```

# export the data
```{r, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# relative humidity data are mainly missing from the data

output.data <- 
  complete.daily.data.radiation %>% 
  select(stn.no.,year, year, day, total.rain, 
         max.temp, min.temp, daily.solar.rad.mj.m2,
         wind.m.s, mean.rh, vpd) %>% 
  filter(!is.na(max.temp)) %>% 
  mutate(year = format(year, scientific = FALSE)) %>% 
  mutate_at(vars(total.rain:vpd), round, 2) %>% 
  ungroup() %>% 
  mutate(year = as.integer(year), day=as.integer(day)) %>% 
  mutate(station = "RPC_Squire") %>% 
  select( "stn.no.","station", "year","day","total.rain",
          "max.temp","min.temp", "daily.solar.rad.mj.m2", 
          "wind.m.s","mean.rh", "vpd")
  
  
short_summary(output.data)

write_csv(output.data, file.path(IntermediateResults, 
                                 paste(output.name, "csv", sep = '.')))

```
















