---
title: "Checking and tiding up the climate data"
author: "Junqi ZHU"
output:
  html_document: default
---

```{r, warning=FALSE, echo=FALSE, tidy=TRUE, error=FALSE, message=FALSE}
 rm(list = ls())
    {
    library(plyr)
    l_ply(list('tidyverse','readxl','tidyr','readr','dplyr','ggplot2','broom','ggthemes','plotly','purrr',
               'reshape2','cowplot','grid', 'reshape2','lubridate', 'RColorBrewer', 'datacheck'), 
          require, character.only = T)
    # tidyverse_update(recursive = FALSE) #updating packages
    #get the current working directory
    MainDir <- list(PROJHOME = normalizePath(getwd()))
    # Input and output directory data file location
    ExpData = file.path(MainDir, 'ExpData')
    # figure output directory, mainly the the place for paper writing 
    FigureOutput = file.path(MainDir, 'Figures')
    
    # Output directory, final results except figures, like statistics, and intermediate data set
    IntermediateResults = file.path(MainDir, 'Intermediate results')  
    SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # CustomizedFunctions = file.path('d:/Programming language/R language/Customized function library/')
    CustomizedFunctions = file.path(MainDir, 'customizedFunctionsLib')
    
    # Load all functions
   # CustomizedFunctions = file.path('/powerplant/workspace/hrmjxz/Programming_lang/R_language/Function_library/')
    CustomizedFunctions = file.path('/mnt/sda/Programming_lang/R_language/Function_library/')
    # CustomizedFunctions = file.path('E:/Programming_lang/R_language/Function_library/')
    IntermediateResults = file.path(MainDir, 'Intermediate results')  
    SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # Load all functions
    source(file.path(CustomizedFunctions,'Customized_functions_for_climate.R'))   
    # lsf.str()  #list of functions
    } 
```

# A remind of the subject that you are working on
```{r}
current.region <- 'Site1003_SEA'
current.subject <- ''
# current.year <- '18_19'
site = "Seaview"
lastYear = '2021'
output.name <- paste(current.region, current.subject, sep = '')
output.name

```

## Load the data
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
options(dplyr.width = Inf, dplyr.print_min = 10)

hourly.data.names <- c("TIMESTAMP",	"SiteID",	"AirTemperatu_Avg",	"AirTemperatu_Min",	
                        "AirTemperatu_Max", "RelativeHumi_Avg", "Rain_Tot",	"Wetness_Avg",
                        "WindSpeed_Avg",	"WindSpeed_Max", "WindSpeed_TMx","WindDirectio_Avg", "WindRun_Tot",
                       "Mean.Solar.Rad.w.m2"
)

# library(openxlsx)

hourly.data.int <- 
  read_csv(file.path(ExpData, 'Site1003_SEA_Hourly.csv')) 
 
hourly.data <-   
  hourly.data.int %>% 
    slice(-c(1:4)) %>% 
    select(1:14) %>% 
    setNames(tolower(hourly.data.names)) %>% 
   # slice(-1) %>% 
   mutate(timestamp = dmy_hm(timestamp)) %>% 
    mutate_if(is.character, funs( as.numeric(as.character(.)))) %>%
   mutate_if(is.factor, funs( as.numeric(as.character(.)))) %>%
    mutate(year=year(timestamp), day = yday(timestamp), hour = hour(timestamp)) %>%    
    distinct(year,day,hour, .keep_all = T) %>% 
  select(-mean.solar.rad.w.m2)

glimpse(hourly.data)
# last(hourly.data$year)

```
## create a complete records of days and hours

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

first.day <- first(hourly.data$day)
first.year <- first(hourly.data$year)

last.day <- last(hourly.data$day)
last.year <- last(hourly.data$year)

start.date <- as.Date(first.day, origin = paste(first.year-1, 12, 31, sep = '-'))
end.date <- as.Date(last.day, origin = paste(last.year-1, 12, 31, sep = '-'))


yday(end.date)
chour <-seq(0,23,by=1)

complete.year.day <- 
  data_frame(date = seq.Date(from = start.date,to = end.date, by = 'day')) %>% 
  mutate(year = year(date), day.of.year = yday(date)) 

 complete.year.day.hour<-  merge(complete.year.day,chour,all=TRUE)
 # data.frame(complete.year.day.hour)
names (complete.year.day.hour) = c("date", "year", "day","hour")


glimpse(complete.year.day.hour)

```
 # Check the missing data and replace missing value
```{r, fig.width=15, fig.height=25,echo=FALSE}
 glimpse(hourly.data)

hourly.data.new <- 
  right_join(hourly.data, complete.year.day.hour, by = c('year','day', 'hour')) %>% 
  
  mutate_at('relativehumi_avg',funs(replace(., .< 0, 0))) %>% 
  mutate_at('relativehumi_avg',funs(replace(., .> 100, 100))) %>%   
  mutate_at('windspeed_avg',funs(replace(., .< 0, 0))) %>% 
  # mutate_at('mean.solar.rad.w.m2',funs(replace(., .< 0, 0))) %>% 
  mutate_if(is.numeric,funs(replace(.,is.nan(.),NA))) %>% 
  
  group_by(day,hour) %>%
  mutate_at(vars(relativehumi_avg:windspeed_avg),funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  mutate_at('airtemperatu_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  # mutate_at('mean.solar.rad.w.m2',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  mutate_at('rain_tot',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  ungroup(.) %>% 
  distinct(year,day, hour, .keep_all = TRUE) %>% 
  arrange(year,day,hour) %>% 
  select(year,day,hour, relativehumi_avg, windspeed_avg, airtemperatu_avg, rain_tot) %>% 
  rename(total.rain = rain_tot) %>% 
  drop_na(airtemperatu_avg)
 

names(hourly.data.new) =c("year", "day", "hour", "mean.rh", 
                          "mean.wind.speed.m.s","mean.ta",                          
                          'total.rain')

glimpse(hourly.data.new)

# hourly.data.new %>% 
#   filter(mean.solar.rad.w.m2 > 1000)

# short_summary(hourly.data.new) 
```
# combine with blenheim radiation data
## add the missing radiation data from the blenheim data
#day	hour	mean.ta	mean.rh	total.radiation.umol.m2.s	CO2.ppm	mean.wind.speed.m.s	swp.MPa	year	stn.no.
```{r,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# relative humidity data are mainly missing from the data
blenheim.radiation <- 
  tbl_df(read.csv(file.path(IntermediateResults, 
                            'MRL_Hourly_New.csv'), header = TRUE))  %>% 
  select(year, day, hour, mean.solar.rad.w.m2) %>% 
  arrange(year, day, hour) %>% 
  group_by(year, day, hour) %>% 
  mutate_at('mean.solar.rad.w.m2',funs(replace(.,is.na(.),mean(.,na.rm=TRUE)))) %>% 
  mutate_at('mean.solar.rad.w.m2',funs(replace(., .<= 1, mean(.,na.rm=TRUE)))) %>% 
  ungroup() 
  
  
glimpse(blenheim.radiation)

complete.radiation <-
  left_join(hourly.data.new, blenheim.radiation, by = c('year','day', 'hour')) %>% 
  drop_na(mean.solar.rad.w.m2)

# complete.radiation %>% 
#   filter(is.na(mean.solar.rad.w.m2))

 short_summary(complete.radiation)  

```



# organize the data for input into GroIMP

```{r, fig.width=15, fig.height=25,echo=FALSE}
# FPAR = 0.55
# WATT_TO_PPFD = 4.55
#     
# date = as.Date("2019-2-04")
# yday(date)
# leap_year(2019)
#   
# climate.data.hourly.new <- 
#   hourly.data.new %>% 
#   
#   arrange(year,day,hour) %>% 
#   mutate(total.radiation.umol.m2.s = as.numeric(mean.solar.rad.w.m2) * WATT_TO_PPFD) %>% 
#   mutate(CO2.ppm = 400, swp.MPa = -0.2, mean.rh = mean.rh/100,stn.no.=97 ) %>% 
#   select(day, hour, mean.ta, mean.rh,total.radiation.umol.m2.s,CO2.ppm, mean.wind.speed.m.s, swp.MPa, year, stn.no.) %>%
#   filter((year >2005))
#     
# write_csv(climate.data.hourly.new, file.path(IntermediateResults, 
#                     paste('SEA.climate.data.hourly.csv',sep = '')))
# range(climate.data.hourly.new$mean.ta)
```


#calculating the daily mean

```{r,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

 climate.data.daily.cal <-
  complete.radiation %>% 
  select(year, day, hour,total.rain,mean.ta, mean.rh,mean.solar.rad.w.m2,mean.wind.speed.m.s) %>%
  mutate(vpd = VPD((mean.ta), mean.rh/100)) %>% 
  group_by(year, day) %>% 
  summarise_all(list(mean=mean,min=min, max=max, sum=sum), na.rm = T) %>% 
  mutate(daily.solar.rad.mj.m2 = mean.solar.rad.w.m2_mean * 3600 *24 /1e6 ) %>%
  select(year, day, total.rain_sum, mean.ta_max, mean.ta_min,mean.ta_mean,
         daily.solar.rad.mj.m2, mean.wind.speed.m.s_mean, mean.rh_mean, vpd_mean) %>% 
  rename(Tmin = mean.ta_min, 
         Tmax = mean.ta_max,
         Tmean = mean.ta_mean,
         totalRain = total.rain_sum,
         Rad = daily.solar.rad.mj.m2, 
         RH  = mean.rh_mean,
         Wind = mean.wind.speed.m.s_mean, 
         vpd = vpd_mean) %>% 
  mutate(ET0 = calcDailyET0(Rad, Tmean, Wind, vpd)) %>% 
  mutate(ET_Rain = ET0 - totalRain) %>% 
  mutate(station = site) %>% 
  mutate(vineyard = case_when(station == "Blenheim" ~ "NA",
                             TRUE ~ station)) %>% 
  mutate(region = "Marlborough") %>% 
  rename(doy = day) %>% 
  filter(!(year == 2005 & doy == 96)) %>% 
  filter(year >=lastYear)

glimpse(climate.data.daily.cal)


# short_summary(climate.data.daily.cal)
write_csv(climate.data.daily.cal, 
          file.path(IntermediateResults, paste(output.name, '.daily.cal.csv',sep = '')))

```


## Load the organized data
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

 daily.data <- 
  read_csv(file.path(IntermediateResults, 'MetData_latest.csv'),guess_max = 5000) %>% 
  arrange(station, year, doy) %>% 
  filter(!(station == site & year >=lastYear))

 daily.data %>%
   filter(station ==site & year>=lastYear)
# daily.data %>%
#    filter(station == 'Seaview') %>% 
#    filter(Rad > 40)

glimpse(daily.data)

```

#join the data
```{r, fig.width=15, fig.height=25,echo=FALSE}

full.data <- 
    bind_rows(daily.data, climate.data.daily.cal) 
 
glimpse(full.data)


 full.data %>%
   filter(station ==site & year>=lastYear)
# short_summary(full.data)
 
 write_csv(full.data, file.path(IntermediateResults, 'MetData_latest.csv'))

# write_tsv(full.data, file.path(IntermediateResults, paste(output.name, "met", sep = '.')))

```

#APSIM output
```{r, fig.width=15, fig.height=25,echo=FALSE}
blenheim.2004 <- 
  full.data %>% 
  filter(station == 'Blenheim' & (year == 2004|year == 2003))

blenheim.2005 <- 
  full.data %>% 
  filter(station == 'Blenheim' & year == 2005 & doy <= 96)

apsim <- 
  full.data %>% 
  filter(station==site) %>% 
  bind_rows(., blenheim.2004) %>% 
  bind_rows(., blenheim.2005) %>% 
  select(year,doy,totalRain,Tmax, Tmin, Rad,Wind,RH,vpd) %>% 
  mutate(totalRain= round(totalRain, 2),
         Tmax = round(Tmax, 2), 
         Tmin = round(Tmin, 2), 
         Rad = round(Rad, 2), 
         Wind = round(Wind, 2), 
         RH = round(RH, 2), 
         vpd = round(vpd,2)) %>% 
  arrange(year, doy)

glimpse(apsim)
# short_summary(apsim)

fileName <- "Site1003_SEA.met"

f <- file(paste0(IntermediateResults,"/", fileName), "w")
    
    cat(
      "[weather.met.weather] \r\n Site = Seaview", "\r\n",
      "Latitude = -41.629",    "\r\n",
      "Longitude = 174.13096", "\r\n",
      "tav=12.76  !annual  average  ambient  temperature", "\r\n",
      "amp=15.19  !annual  amplitud  in  mean  monthly  temperature", "\r\n",    
      "year  day  rain  maxt  mint  radn  wind rh vpd", "\r\n",
      "()  ()  (mm)  (oC)  (oC)  (MJ/m2/d)  (m/s) (%) (kpa)", "\r\n",
      
      file= f, append = T)
    
    write.table(apsim, file = f, append = TRUE, quote = FALSE,
                sep = " ", eol = "\r\n", col.names = F, row.names=F)
    # 
    close(f)


# write_tsv(full.data, file.path(IntermediateResults, paste(output.name, "met", sep = '.')))

# 
# write.table(apsim, file.path(IntermediateResults, paste(output.name, "met", sep = '.')), row.names = F, sep = ' ')

# write_tsv(full.data, file.path(IntermediateResults, paste(output.name, "met", sep = '.')))

```














 
 
 
 