---
title: "Checking and tiding up the climate data"
author: "Junqi ZHU"
output:
  html_document: default
---

```{r, warning=FALSE, echo=FALSE, tidy=TRUE, error=FALSE, message=FALSE}
 rm(list = ls())
    {
    library(plyr)
    l_ply(list('tidyverse','readxl','tidyr','readr','dplyr','ggplot2','broom','ggthemes','plotly','purrr',
               'reshape2','cowplot','grid', 'reshape2','lubridate', 'RColorBrewer', 'datacheck'), 
          require, character.only = T)
    # tidyverse_update(recursive = FALSE) #updating packages
    #get the current working directory
    MainDir <- list(PROJHOME = normalizePath(getwd()))
    # Input and output directory data file location
    ExpData = file.path(MainDir, 'ExpData')
    # figure output directory, mainly the the place for paper writing 
    FigureOutput = file.path(MainDir, 'Figures')
    
    # Output directory, final results except figures, like statistics, and intermediate data set
    IntermediateResults = file.path(MainDir, 'Intermediate results')  
    SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # CustomizedFunctions = file.path('d:/Programming language/R language/Customized function library/')
    CustomizedFunctions = file.path(MainDir, 'customizedFunctionsLib')
    
   CustomizedFunctions = file.path('/powerplant/workspace/hrmjxz/Programming_lang/R_language/Function_library/')
    IntermediateResults = file.path(MainDir, 'Intermediate results')  
    SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # Load all functions
    source(file.path(CustomizedFunctions,'Customized_functions_for_climate.R'))
    # lsf.str()  #list of functions
    } 
```

# A remind of the subject that you are working on
```{r}
current.region <- 'WRV'

current.subject <- ''
# current.year <- '18_19'
site = "WairauValley"
output.name <- paste(current.region, current.subject, sep = '')
output.name

```

## Load the data
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
options(dplyr.width = Inf, dplyr.print_min = 10)

#TIMESTAMP	RECORD	SiteID	AirTemperatu_Avg	AirTemperatu_Min	AirTemperatu_Max	RelativeHumi_Avg	Rain_Tot	Wetness_Avg	WindSpeed_Avg	WindSpeed_Max	WindSpeed_TMx	WindDirectio_Avg	BatteryVoltage

hourly.data.names <- c("TIMESTAMP",	"RECORD","SiteID",	"AirTemperatu_Avg",	"AirTemperatu_Min",	
                        "AirTemperatu_Max", "RelativeHumi_Avg", "Rain_Tot",	"Wetness_Avg",
                        "WindSpeed_Avg",	"WindSpeed_Max","WindSpeed_TMx",'WindDirectio_Avg',"BatteryVoltage"
)


 
hourly.data.int <- 
  read_csv(file.path(ExpData, 'WRV New hourly.csv')) 
 

hourly.data <-   
  hourly.data.int %>% 
  # select(1:23) %>% 
  slice(-c(1:7)) %>%
    setNames(tolower(hourly.data.names)) %>% 
   # slice(-1) %>% 
    mutate(timestamp = mdy_hm(timestamp)) %>% 
    mutate_if(is.character, funs( as.numeric(as.character(.)))) %>%
    mutate(year=year(timestamp), day = yday(timestamp), 
           hour = hour(timestamp)) %>% 
        distinct(year,day,hour, .keep_all = T)

glimpse(hourly.data)
# last(hourly.data$year)

```

## create a complete records of days

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

first.day <- first(hourly.data$day)
first.year <- first(hourly.data$year)

last.day <- last(hourly.data$day)
last.year <- last(hourly.data$year)

start.date <- as.Date(first.day, origin = paste(first.year-1, 12, 31, sep = '-'))
end.date <- as.Date(last.day, origin = paste(last.year-1, 12, 31, sep = '-'))


yday(end.date)
chour <-seq(0,23,by=1)

complete.year.day <- 
  data_frame(date = seq.Date(from = start.date,to = end.date, by = 'day')) %>% 
  mutate(year = year(date), day.of.year = yday(date)) 

 complete.year.day.hour<-  merge(complete.year.day,chour,all=TRUE)
 data.frame(complete.year.day.hour)
names (complete.year.day.hour) = c("date", "year", "day","hour")


glimpse(complete.year.day.hour)

```

# Check the missing data and replace missing value
```{r, fig.width=15, fig.height=25,echo=FALSE}
 
names(hourly.data)
hourly.data.new <- 
  right_join(hourly.data, complete.year.day.hour, by = c('year','day', 'hour')) %>% 
  mutate_at('relativehumi_avg',funs(replace(., .< 0, 0))) %>% 
  mutate_at('relativehumi_avg',funs(replace(., .> 100, 100))) %>%   
  mutate_at('windspeed_avg',funs(replace(., .< 0, 0))) %>% 
  mutate_at('airtemperatu_avg',funs(replace(., .< -10, NA))) %>% 
  mutate_at('rain_tot',funs(replace(., .< 0, 0))) %>% 
  mutate_at('rain_tot',funs(replace(., is.nan(.), 0))) %>%
  mutate_at('windspeed_avg',funs(replace(.,is.na(.),NA))) %>% 
  mutate_if(is.numeric,funs(replace(.,is.nan(.),NA))) %>% 
  group_by(day,hour) %>%
  mutate_at('windspeed_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE)))) %>% 
  mutate_at(vars(relativehumi_avg:windspeed_avg),funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  mutate_at('airtemperatu_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  ungroup(.) %>% 
  distinct(year,day, hour, .keep_all = TRUE) %>% 
  arrange(year,day,hour) %>% 
  select(siteid, year,day,hour, relativehumi_avg, windspeed_avg, airtemperatu_avg, rain_tot) %>% 
  mutate_at('windspeed_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE)))) %>% 
  mutate(siteid = 100)
 
 names(hourly.data.new) =c("stn.no.", "year", "day", "hour", "mean.rh", "mean.wind.speed.m.s","mean.ta", 'total.rain')

 glimpse(hourly.data.new)

 short_summary(hourly.data.new)  
 
 # hourly.data.new %>% 
 #   filter(is.na(mean.wind.speed.m.s))
  # View(hourly.data.hourly)
```


 

# combine with blenheim radiation data
## add the missing radiation data from the blenheim data
#day	hour	mean.ta	mean.rh	total.radiation.umol.m2.s	CO2.ppm	mean.wind.speed.m.s	swp.MPa	year	stn.no.
# combine with blenheim radiation data
## add the missing radiation data from the blenheim data
#day	hour	mean.ta	mean.rh	total.radiation.umol.m2.s	CO2.ppm	mean.wind.speed.m.s	swp.MPa	year	stn.no.
```{r,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# relative humidity data are mainly missing from the data
blenheim.radiation <- 
  tbl_df(read.csv(file.path(IntermediateResults, 
                            'MRL_Hourly_New.csv'), header = TRUE))  %>% 
  select(year, day, hour, mean.solar.rad.w.m2) %>% 
  arrange(year, day, hour) %>% 
  mutate_at('mean.solar.rad.w.m2',funs(replace(.,is.na(.),mean(.,na.rm=TRUE)))) %>% 
  ungroup() %>% 
  mutate(hour = hour/100)
   

glimpse(blenheim.radiation)

complete.radiation <-
  left_join(hourly.data.new, blenheim.radiation, by = c('year','day', 'hour')) 


# short_summary(complete.radiation)  

```


<!-- #organize the data for input into GroIMP  -->
<!-- ```{r, fig.width=15, fig.height=25,echo=FALSE} -->
<!-- FPAR = 0.55 -->
<!-- WATT_TO_PPFD = 4.55 -->

<!-- date = as.Date("2019-2-04") -->
<!-- yday(date) -->
<!-- leap_year(2019) -->

<!-- climate.data.hourly <-  -->
<!--   complete.radiation %>%  -->

<!--   mutate(stn.no. = 100) %>% -->
<!--   mutate(CO2.ppm = 400, swp.MPa = -0.2, mean.rh = mean.rh/100) %>%  -->
<!--      select(day, hour, mean.ta, mean.rh,total.radiation.umol.m2.s,CO2.ppm, mean.wind.speed.m.s, swp.MPa, year, stn.no.) #%>% -->
<!--   #filter((year == 2019)) -->

<!-- write_csv(climate.data.hourly, file.path(IntermediateResults,  -->
<!--                     paste('WRV.climate.data.hourly.csv',sep = '')))         -->
<!-- names(climate.data.hourly) -->
<!-- range(climate.data.hourly$mean.ta) -->
<!--   range(climate.data.hourly$stn.no.) -->
<!-- ``` -->

# daily calculation
```{r, fig.width=15, fig.height=25,echo=FALSE}

 climate.data.daily.cal <-
  complete.radiation %>% 
  select(year, day, hour,total.rain,mean.ta, mean.rh,mean.solar.rad.w.m2,mean.wind.speed.m.s) %>% 
  drop_na(mean.solar.rad.w.m2) %>% 
  mutate(vpd = VPD((mean.ta), mean.rh/100)) %>% 
  group_by(year, day) %>% 
  summarise_all(list(mean=mean,min=min, max=max, sum=sum), na.rm = T) %>% 
  mutate(daily.solar.rad.mj.m2 = mean.solar.rad.w.m2_mean * 3600 *24 /1e6 ) %>%
  select(year, day, total.rain_sum, mean.ta_max, mean.ta_min,mean.ta_mean,
         daily.solar.rad.mj.m2, mean.wind.speed.m.s_mean, mean.rh_mean, vpd_mean) %>% 
  rename(Tmin = mean.ta_min, 
         Tmax = mean.ta_max,
         Tmean = mean.ta_mean,
         totalRain = total.rain_sum,
         Rad = daily.solar.rad.mj.m2, 
         RH  = mean.rh_mean,
         Wind = mean.wind.speed.m.s_mean, 
         vpd = vpd_mean) %>% 
  mutate(ET0 = calcDailyET0(Rad, Tmean, Wind, vpd)) %>% 
  mutate(ET_Rain = ET0 - totalRain) %>% 
  mutate(station = site) %>% 
  mutate(vineyard = case_when(station == "Blenheim" ~ "NA",
                             TRUE ~ station)) %>% 
  mutate(region = "Marlborough") %>% 
  rename(doy = day)


glimpse(climate.data.daily.cal)

write_csv(climate.data.daily.cal, 
          file.path(IntermediateResults, paste(output.name, '.daily.cal.csv',sep = '')))

```


## Load the organized data
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

 daily.data <- 
  read_csv(file.path(IntermediateResults, 'MetData_2020_5.csv'),guess_max = 1000) 

glimpse(daily.data)

```

#join the data
```{r, fig.width=15, fig.height=25,echo=FALSE}

full.data <- 
    bind_rows(daily.data, climate.data.daily.cal) 
 
# short_summary(full.data)
 
 # write_csv(full.data, file.path(IntermediateResults, 'MetData_2020_5.csv'))

# write_tsv(full.data, file.path(IntermediateResults, paste(output.name, "met", sep = '.')))
glimpse(full.data)
```

#APSIM output
```{r, fig.width=15, fig.height=25,echo=FALSE}

apsim <- 
  full.data %>% 
  filter(station==site) %>% 
  select(year,doy,totalRain,Tmax, Tmin, Rad,Wind,RH,vpd) %>% 
  mutate(RH = round(RH, 2), vpd = round(vpd,2))

glimpse(apsim)
write.table(apsim, file.path(IntermediateResults, paste(output.name, "met", sep = '.')), row.names = F, sep = ' ')

# write_tsv(full.data, file.path(IntermediateResults, paste(output.name, "met", sep = '.')))

```