---
title: "Oyster Bay Sauvignon blanc"
author: "Yao Liu & Junqi ZHU"
date: "04/04/2023"
output:
  word_document: default
---
# Case: Oyster Bay Sauvignon blanc

```{r, warning=FALSE, echo=FALSE, tidy=TRUE, error=FALSE, message=FALSE}
 rm(list = ls())
    {
    library(plyr)
    l_ply(list('tidyverse','readxl','ggplot2','readr','tidyr','dplyr','dbplyr','purrr','broom','ggthemes','plotly','RcppRoll','MASS',
               'caret','ggpubr','compare','gtable','grid','viridis','reshape2','cowplot','lubridate', 'RColorBrewer', 'datacheck',
               'openair','knitr','zoo','SciViews','data.table', 'janitor','RSQLite','ggthemes'),
          require, character.only = T)
    # tidyverse_update(recursive = FALSE) 
    #get the current working directory
    MainDir <- list(PROJHOME = normalizePath(getwd()))
    # Input and output directory data file location
    InputData = file.path(MainDir, 'InputData')
    # Input and output directory data file location
    OutputData = file.path(MainDir, 'OutputData')
    # figure output directory, mainly the the place for paper writing 
    FigureOutput = file.path(MainDir, 'Figures')
    
    CustomizedFunctions = file.path(MainDir,'Functions')
    #IntermediateResults = file.path(MainDir, 'Intermediate results')  
    #SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # Load all functions
    source(file.path(CustomizedFunctions,'Abundance_conidia.R'))
    source(file.path(CustomizedFunctions,'Calculate_DAWS.R'))
    source(file.path(CustomizedFunctions,'Compare_BBCH_DAWS.R'))
    source(file.path(CustomizedFunctions,'General_functions.R'))
    source(file.path(CustomizedFunctions,'Create_New_Managements.R'))
    } 
```

```{r setup, include=FALSE}
options(scipen=999)
  
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", 
                      fig.width = 14, fig.height = 10, dpi = 300)
#Constants
outlier.colour = "#ff0000"

```

```{r,warning=FALSE, echo=FALSE, error=FALSE}
#'Site1004_RPC', 'Site1002_OYB','Site1003_SEA','Site1001_BRA'
current.region <- 'Site1002_OYB_Hourly'   
current.subject <- 'Sauvignon blanc'

#'Squire','Oyster Bay','Seaview', 'Booker'
site = 'OYB'
lastYear = '2004'

input.name <- paste0(current.region, ".csv")
output.name <- paste(current.region, current.subject, sep = '_')
#glimpse(output.name)
```

### Load the data 

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
climate.data.names <- c('ID','Year','Day','Hour','Tmean','RH','Wetness','Rain','T_grass','Tmin_grass',
                        'T_soil','Tmin_soil','Radation','WindSpeed','WindDirection','PET','GDD>10','GDD1-Sep')
  
climate.data <- read_csv(file.path(InputData,input.name)) %>% 
  dplyr::select(1:18) %>% 
  slice(-c(1:7)) %>% 
  setNames(tolower(climate.data.names)) %>% 
#  mutate(Timestamp=as.POSIXct(timestamp,format="%d/%m/%Y %H:%M"),
#         year=year(Timestamp),day=yday(Timestamp),hour=hour(Timestamp)) %>% 
  mutate_all(., funs( as.numeric(as.character(.)))) %>% 
  mutate(hour = hour/100 - 1) %>%
  distinct(year,day,hour, .keep_all = T) %>% 
  dplyr::filter(year>= lastYear) 
  # filter(!(year==2020 & day<=11))
  
#glimpse(climate.data)
#last(climate.data$year)

```

### create a complete records of days and hours

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

first.day <- first(climate.data$day)
first.year <- first(climate.data$year)

last.day <- last(climate.data$day)
last.year <- last(climate.data$year)

start.date <- as.Date(first.day, origin = paste(first.year-1, 12, 31, sep = '-'))
end.date <- as.Date(last.day, origin = paste(last.year-1, 12, 31, sep = '-'))


#yday(end.date)
#chour <-c(0,100,200,300,400,500,600,700,800,900,1000,1100,1200,
#          1300,1400,1500,1600,1700,1800,1900,2000,2100,2200,2300)
chour <-c(0,1,2,3,4,5,6,7,8,9,10,11,12,
          13,14,15,16,17,18,19,20,21,22,23)

complete.year.day <- 
  data_frame(date = seq.Date(from = start.date,to = end.date, by = 'day')) %>% 
  mutate(year = year(date), day.of.year = yday(date)) 

complete.year.day.hour<-  data.frame(merge(complete.year.day,chour,all=TRUE))
#data.frame(complete.year.day.hour)
names (complete.year.day.hour) = c("date", "year", "day","hour")

#glimpse(complete.year.day.hour)

```

### Check the missing data and replace missing value

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

complete.hourly <-
  right_join(climate.data, complete.year.day.hour, by = c('year','day', 'hour')) %>%
  mutate_at('rh',funs(replace(., .< 0, 0))) %>%
  mutate_at('rh',funs(replace(., .> 100, 100))) %>%
  mutate_at('wetness',funs(replace(., .< 0, 0))) %>%
  mutate_at('wetness',funs(replace(., .> 100, 100))) %>%  
  mutate_if(is.numeric,funs(replace(.,is.nan(.),NA))) %>% 
  group_by(day,hour) %>%
  mutate_at('rh',funs(replace(.,is.na(.),mean(.,na.rm=TRUE)))) %>%
  mutate_at('tmean',funs(replace(.,is.na(.),mean(.,na.rm=TRUE)))) %>%
  mutate_at('rain',funs(replace(.,is.na(.),0))) %>%
  mutate_at('rain',funs(replace(., . < 0 ,0))) %>%
  ungroup(.) %>% 
  drop_na(year) %>% 
#  mutate(hour = hour/100) %>% 
  arrange(year, day, hour)

#write_csv(complete.hourly, file.path(OutputData, paste(output.name, 'hourly.csv',sep = '')))

#short_summary(complete.hourly)  


# Step 1: Set wetness < 0 to 0 and wetness > 100 to 100
#complete.hourly$wetness[complete.hourly$wetness < 0] <- 0
#complete.hourly$wetness[complete.hourly$wetness > 100] <- 100

# Step 2: Create new variable wetnessBinary
complete.hourly$wetnessBinary <- ifelse(complete.hourly$wetness >= 50, 1, 0)

# Step 3: Calculate wetnessDuration for each day
climate.data.daily.cal  <- complete.hourly %>%
  group_by(year, day) %>%
  mutate(wetnessBinary = ifelse(wetness >= 50, 1, 0),
         wetnessDuration = ifelse(wetnessBinary == 1 & lag(wetnessBinary, default = 0) == 0, 0, cumsum(wetnessBinary)) * wetnessBinary) %>%
  summarize(tmin = min(tmean, na.rm = TRUE),
            tmax = max(tmean, na.rm = TRUE),
            tmean = mean(tmean, na.rm = TRUE),
            rh = mean(rh, na.rm = TRUE),
            wetness = mean(wetness, na.rm = TRUE),
            rain = sum(rain, na.rm = TRUE),
            wetness_duration = ifelse(max(wetnessDuration, na.rm = TRUE) >= 4, max(wetnessDuration, na.rm = TRUE), 0)) %>%
  ungroup() %>% 
  dplyr::rename(doy = day) 
#%>%   filter(year >=lastYear)      

# Step 4: Rename columns
colnames(climate.data.daily.cal) <- c('year','doy','Tmin','Tmax','Tmean','RH','wetness','Rain','WD')

#write_csv(climate.data.daily.cal, 
#          file.path(OutputData, paste(site,current.subject, 'meteodata.csv',sep = '_')))

```

## Calculate CISO

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
## Calculate the relative abundance of conidia on sources (7-day period)

Cal_daily <- climate.data.daily.cal
#Cal_daily$RH =  Cal_daily$RH/100 
Tmin_spor = 0
Tmin_mygr = 0
Tmax_spor = 35
Tmax_mygr = 40 

CISO =  data.frame()

for (id in 1 : max(seq_len(nrow(Cal_daily)))) {
#for(id in 1:nrow(Cal_daily)) {
  Temp_CISO = Cal_daily[id,]
  
  Temp_CISO$Teq = Cal_Teq(Temp_CISO$Tmean, Temp_CISO$Tmin, Temp_CISO$Tmax)
  Temp_CISO$Teq_spor = Cal_Teq(Temp_CISO$Tmean, Tmin_spor, Tmax_spor)
  Temp_CISO$Teq_mygr = Cal_Teq(Temp_CISO$Tmean, Tmin_mygr, Tmax_mygr)
  
  if (all(!is.na(Temp_CISO[c("RH", "Rain")])) && (Temp_CISO$RH >= 90 | Temp_CISO$Rain >= 0.2)) {
    Temp_CISO$Mf = Temp_CISO$WD/24.0
  } else {
    Temp_CISO$Mf = 0
  } 
  
  Temp_CISO$MYGR = Cal_MYGR(Temp_CISO$Teq_mygr, Temp_CISO$Mf)
  Temp_CISO$SPOR = Cal_SPOR(Temp_CISO$Teq_spor, Temp_CISO$RH)

  CISO =  bind_rows(CISO,Temp_CISO)
  
}

CISO$CISO = Cal_CISO(CISO$MYGR, CISO$SPOR)

```

## Determine BBCH stage by using Grapevine.Phenology.Stage in APSIM file

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
# Determine BBCH stage by using Grapevine.Phenology.Stage in APSIM file 

#Report <- read_csv(file.path(InputData,'Report0.csv')) #%>% 
#Grapevine <- dbConnect(SQLite(),file.path(InputData, "Squire Sauvignon blanc.db"), ":memory:") #%>%


# Get table
#Report1 <- dbReadTable(Grapevine, "Report")
#write_csv(Report,file.path(OutputData, "Report.csv", sep = ''))

# Read the Excel file into R as a data frame
Report <- read_excel(file.path(InputData, paste0("/","Apsim_report","/","Oyster Bay Sauvignon blanc.xlsx")), sheet = "Report")

Report_Code_BBCH <- Match_BBCH_APSIM(Report)

#df_BBCH <- read_excel(file.path(InputData, 'BBCH.xlsx')) 
GS_data = data.frame()

Date_pre <-
    CISO %>%
#    mutate(year = year(date), doy= doy) %>% 
    do(DOY.from.July1st(.))
  
for (idc in 1:nrow(Date_pre)) {
  Gs_CISO = Date_pre[idc,]
  Gs_CISO$GS = Compare_BBCH_DAWS(Gs_CISO,Report_Code_BBCH)
  GS_data = bind_rows(GS_data,Gs_CISO)
}  

#GS_data1 <- GS_data

```

# calculate RISK

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

# The model calculations begin when grape inflorescences are clearly visible and ends when berries are ripe for harvest, with a time step of 1 day.
Risk_data = data.frame()

for (idr in 1:nrow(GS_data)) {
  Temp_Risk = GS_data[idr,]
  Temp_Risk$RIS1 = NA
  Temp_Risk$RIS2 = NA
  Temp_Risk$RIS3 = NA
  Temp_Risk$SUS1 = NA
  Temp_Risk$SUS2 = NA
  Temp_Risk$SUS3 = NA
  Temp_Risk$INF1 = NA
  Temp_Risk$INF2 = NA
  Temp_Risk$INF3 = NA

  if (!is.na(Temp_Risk$GS) & Temp_Risk$GS >= 53 & Temp_Risk$GS <= 73) {
    ## in the first infection window(stage 53-73),calculate an infection rate on inflorescences and young clusters
    Temp_Risk$SUS1 = Cal_RIS1(Temp_Risk$CISO, Temp_Risk$Teq, Temp_Risk$WD, Temp_Risk$GS)[[1]]
    Temp_Risk$INF1 = Cal_RIS1(Temp_Risk$CISO, Temp_Risk$Teq, Temp_Risk$WD, Temp_Risk$GS)[[2]]
    Temp_Risk$RIS1 = Cal_RIS1(Temp_Risk$CISO, Temp_Risk$Teq, Temp_Risk$WD, Temp_Risk$GS)[[3]]

  } 
  
  if (!is.na(Temp_Risk$GS) & Temp_Risk$GS >= 79 & Temp_Risk$GS <= 89) {
    
    # (stage 79-89) in the second infection window,calculate two infection rates on ripening berries: one for conidial infection(INF2) and another for berry-to-berry infection(INF3)
    # Infection rate for conidia infection:
    Temp_Risk$SUS2 = Cal_RIS2(Temp_Risk$CISO, Temp_Risk$Teq, Temp_Risk$WD, Temp_Risk$GS)[[1]]
    Temp_Risk$INF2 = Cal_RIS2(Temp_Risk$CISO, Temp_Risk$Teq, Temp_Risk$WD, Temp_Risk$GS)[[2]]
    Temp_Risk$RIS2 = Cal_RIS2(Temp_Risk$CISO, Temp_Risk$Teq, Temp_Risk$WD, Temp_Risk$GS)[[3]]

     ## Infection rate for berry-to-berry infection:
    Temp_Risk$SUS3 = Cal_RIS3(Temp_Risk$MYGR, Temp_Risk$Teq, Temp_Risk$RH, Temp_Risk$GS)[[1]]
    Temp_Risk$INF3 = Cal_RIS3(Temp_Risk$MYGR, Temp_Risk$Teq, Temp_Risk$RH, Temp_Risk$GS)[[2]]
    Temp_Risk$RIS3 = Cal_RIS3(Temp_Risk$MYGR, Temp_Risk$Teq, Temp_Risk$RH, Temp_Risk$GS)[[3]]

  } 
  
  Risk_data = bind_rows(Risk_data,Temp_Risk)
  
}
```

## Calculate accumulated severity

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

SEV_data <-  Risk_data %>%
    mutate_at(vars(c('RIS1','RIS2','RIS3')),funs(replace(.,is.na(.),0))) %>%
    group_by(season) %>%
    mutate(
           SEV1 = cumsum(RIS1),
           SEV2 = cumsum(RIS2),
           SEV3 = cumsum(RIS3),
           SEV23 = cumsum(RIS2+RIS3)
  )
SEV_data$date =as.Date(parse_date_time( paste(SEV_data$year, SEV_data$doy), orders = "yj"))
SEV_data$variety = current.subject
SEV_data$site = site 

write_csv(SEV_data,file.path(OutputData, paste(output.name, '.csv',sep = '')))

figure_number <- 1
```


### Fig. `r figure_number` SPOR Plot

```{r SPOR_Plot, fig.cap = "SPOR Plot.", echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE}

## test plot
plot_A = subset(SEV_data,season == "2020-2021")

colors = c('#5470C6', '#91CC75', '#EE6666', '#ff7f00')  
my_theme = theme(panel.grid = element_blank(), panel.background = element_rect(fill = NA))

##05-1 plot geom_area
A = ggplot(plot_A,aes(x = date, y = SPOR))  + 
  geom_area(fill="Grey",position="stack") +
  scale_x_date(limits = c(as.Date("2020-10-01"), as.Date("2021-07-01")),date_breaks = "1 month",
               date_labels = "%b") +
#    scale_x_date(limits = c(as.Date("2021-01-01"), as.Date("2022-12-11")),date_breaks = "1 month",
#               date_labels = "%b") +
  theme_economist() +
  theme(panel.grid = element_blank(), 
        panel.background = element_rect(fill = NA), 
        axis.text.y = element_text(color = "black"), 
        axis.ticks.y = element_line(color = "black"), 
        axis.title.y = element_text(color = "black", angle = 90), 
        axis.line.y = element_line(color = "black"), 
        axis.line.x = element_line(color = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.x = element_text(color = "red")
  ) + 
  ggtitle("SPOR Plot") 

plot(A)

figure_number = figure_number + 1

```

# Fig. `r figure_number` Infection severity

```{r Infection severity, fig.cap = "Infection severity.", echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE}
##05-2 plot Bar & line
plot_B = subset(SEV_data,season == "2020-2021")

colors = c('#5470C6', '#91CC75', '#EE6666', '#ff7f00')  
#my_theme = theme(panel.grid = element_blank(), panel.background = element_rect(fill = NA))

B = ggplot(plot_B, aes(x = date)) + 
  geom_col(aes(y = RIS1, fill = "RIS1"), width = 1.5, position = position_nudge(x = -0.2)) +
  geom_col(aes(y = RIS2, fill = "RIS2"), width = 1.5, position = position_nudge(x = -0.2)) +
  geom_col(aes(y = RIS3, fill = "RIS3"), width = 1.5, position = position_nudge(x = -0.2)) +
  geom_line(aes(y = SEV1, color = "SEV1"), linewidth = 1, position = position_nudge(x = -0.2)) +
  geom_line(aes(y = SEV23, color = "SEV23"), linewidth = 0.8, position = position_nudge(x = -0.2)) +
  scale_x_date(
    limits = c(as.Date("2020-10-01"), as.Date("2021-07-01")),
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  scale_y_continuous(
    name = "Infection severity (RIS)",
    sec.axis = sec_axis(~. * 1, name = "Accumulated severity (SEV)")
  ) +
  scale_fill_manual(values = colors, labels = c("RIS1", "RIS2", "RIS3")) +
  scale_color_manual(values = c("red", "black"), labels = c("SEV1", "SEV23")) +
  theme_economist() +
  theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = NA),
    axis.text.y = element_text(color = "black"),
    axis.ticks.y = element_line(color = "black"),
    axis.title.y = element_text(color = "black", angle = 90),
    axis.title.y.right = element_text(color = "black", angle = 90),
    axis.line.y = element_line(color = "black"),
    axis.line.x = element_line(color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
  ) +
  labs(
    title = "Infection Severity",
    fill = "RIS Categories",
    color = "SEV Categories",
    subtitle = unique(plot_B$season) 
  )

plot(B)


figure_number = figure_number + 1

```


# Fig. `r figure_number` Weather change

```{r Weather change,  fig.cap = "Weather change.", fig.align = 'center', out.height= "100%", out.width="100%", fig.fullwidth=FALSE, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
##05-4 plot line & Bar & geom_area
plot_D = subset(SEV_data,season == "2020-2021")

colors = c('#5470C6', '#91CC75', '#EE6666', '#ff7f00')  
my_theme = theme(panel.grid = element_blank(), panel.background = element_rect(fill = NA))

D = ggplot(plot_D, aes(x = date)) + 
  geom_line(aes(y = Tmean), linewidth = 2, color = "black",position = position_nudge(x = -0.2)) +
  geom_line(aes(y = RH/100), linewidth = 2,  color = "green", position = position_nudge(x = -0.2)) +
  geom_col(aes(y = Rain),fill = "blue", width = 1.5, position = position_nudge(x = -0.2)) +
  geom_col(aes(y = WD),fill = "grey", width = 1.5, position = position_nudge(x = -0.2)) +
  scale_x_date(limits = c(as.Date("2020-10-01"), as.Date("2021-07-01")),date_breaks = "1 month",
               date_labels = "%b") +
#  scale_X_continuous(limits = c(as.Date("2021-07-01"), as.Date("2022-07-01")),date_breaks = "1 month")+
#  scale_y_continuous(
#    name = "T(°C)/WD(hours)",  breaks=(seq(0, 30, 5)),sec.axis = sec_axis(trans=~.*3,,name = "RH(%)/Rain(mm)")) +
  theme_economist() +
  theme(panel.grid = element_blank(), 
        panel.background = element_rect(fill = NA), 
        axis.text.y = element_text(color = "black"), 
        axis.ticks.y = element_line(color = "black"), 
        axis.title.y = element_text(color = "black", angle = 90), 
        axis.title.y.right = element_text(color = "black", angle = 90),
        axis.line.y = element_line(color = "black"), 
        axis.line.x = element_line(color = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.x = element_text(color = "red"),
  ) +
  ggtitle("D")

plot(D)

figure_number = figure_number + 1

```

