---
title: "Checking and tiding up the climate data"
author: "Junqi ZHU"
output:
  html_document: default
---

```{r, warning=FALSE, echo=FALSE, tidy=TRUE, error=FALSE, message=FALSE}
 rm(list = ls())
    {
    library(plyr)
    l_ply(list('tidyverse','readxl','tidyr','readr','dplyr','ggplot2','broom','ggthemes','plotly','purrr',
               'reshape2','cowplot','grid', 'reshape2','lubridate', 'RColorBrewer', 'datacheck'), 
          require, character.only = T)
    # tidyverse_update(recursive = FALSE) #updating packages
    #get the current working directory
    MainDir <- list(PROJHOME = normalizePath(getwd()))
    # Input and output directory data file location
    ExpData = file.path(MainDir, 'ExpData')
    # figure output directory, mainly the the place for paper writing 
    FigureOutput = file.path(MainDir, 'Figures')
    
    # Output directory, final results except figures, like statistics, and intermediate data set
    IntermediateResults = file.path(MainDir, 'Intermediate results')  
    SupportingFunctions = file.path(MainDir, 'Supporting functions')
    # CustomizedFunctions = file.path('d:/Programming language/R language/Customized function library/')
    CustomizedFunctions = file.path(MainDir, 'customizedFunctionsLib')
    
    # Load all functions
    source(file.path(CustomizedFunctions,'Customized_curve_fitting_functions.R'))
    source(file.path(CustomizedFunctions,'Customized_functions_data_reconstruction.R'))
    
    source(file.path(SupportingFunctions,'Layout_of_ggplot.R'))
    source(file.path(SupportingFunctions,'Specific_functions.R'))
    # lsf.str()  #list of functions
    } 
```

# A remind of the subject that you are working on
```{r}
current.region <- 'Site1004_RPC'
current.subject <- 'Hourly_New'
# current.year <- '18_19'

output.name <- paste(current.region, current.subject, sep = '_')
output.name

```

## Load the data
```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}
options(dplyr.width = Inf, dplyr.print_min = 10)

hourly.data.names <- c("TIMESTAMP",		"SiteID",	"AirTemperatu_Avg",	"AirTemperatu_Min",	
                        "AirTemperatu_Max", "RelativeHumi_Avg", "Rain_Tot",	"Wetness_Avg",
                        "WindSpeed_Avg",	"WindSpeed_Max")


hourly.data.int <- 
  read_csv(file.path(ExpData, 'Site1004_RPC_Hourly.csv')) 


hourly.data <-   
  hourly.data.int %>% 
    slice(-c(1:4)) %>% 
    select(1:10) %>% 
    setNames(tolower(hourly.data.names)) %>% 
    slice(-1) %>% 
   mutate(timestamp = dmy_hm(timestamp)) %>%
   mutate_if(is.character, funs( as.numeric(as.character(.)))) %>%
    mutate(year=year(timestamp), day = yday(timestamp), 
           hour = hour(timestamp)) %>% 
   # mutate(date = convertToDate(timestamp, origin = "1900-01-01")) %>% 
   # mutate(hour = round(timestamp%%1 *24)) %>% 
    distinct(year,day,hour, .keep_all = T)

 glimpse(hourly.data)
 

```
## create a complete records of days and hours

```{r, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE}

first.day <- first(hourly.data$day)
first.year <- first(hourly.data$year)

last.day <- last(hourly.data$day)
last.year <- last(hourly.data$year)

start.date <- as.Date(first.day, origin = paste(first.year-1, 12, 31, sep = '-'))
end.date <- as.Date(last.day, origin = paste(last.year-1, 12, 31, sep = '-'))


yday(end.date)
chour <-seq(0,23,by=1)

complete.year.day <- 
  data_frame(date = seq.Date(from = start.date,to = end.date, by = 'day')) %>% 
  mutate(year = year(date), day.of.year = yday(date)) 

 complete.year.day.hour<-  merge(complete.year.day,chour,all=TRUE)
 data.frame(complete.year.day.hour)
names (complete.year.day.hour) = c("date", "year", "day","hour")


glimpse(complete.year.day.hour)

```
# Check the missing data and replace missing value
```{r, fig.width=15, fig.height=25,echo=FALSE}
 

hourly.data.new <- 
  right_join(hourly.data, complete.year.day.hour, by = c('year','day', 'hour')) %>% 
  mutate_at('relativehumi_avg',funs(replace(., .< 0, 0))) %>% 
  mutate_at('relativehumi_avg',funs(replace(., .> 100, 100))) %>%   
  mutate_at('windspeed_avg',funs(replace(., .< 0, 0))) %>% 
  mutate_at('airtemperatu_avg',funs(replace(., .< -10, NA))) %>% 
  
  mutate_if(is.numeric,funs(replace(.,is.nan(.),NA))) %>%
  
  group_by(day,hour) %>%
  
  mutate_at('airtemperatu_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  mutate_at('relativehumi_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  mutate_at('windspeed_avg',funs(replace(.,is.na(.),mean(.,na.rm=TRUE))))%>%
  
  ungroup(.) %>% 
  
  distinct(year,day, hour, .keep_all = TRUE) %>% 
  arrange(year,day,hour) %>% 
  select(siteid, year,day,hour, relativehumi_avg, windspeed_avg, airtemperatu_avg)

 names(hourly.data.new) =c("stn.no.", "year", "day", "hour", "mean.rh", "mean.wind.speed.m.s","mean.ta")

glimpse(hourly.data.new)

short_summary(hourly.data.new)  
 
  # View(hourly.data.hourly)
```

# combine with blenheim radiation data
## add the missing radiation data from the blenheim data
#day	hour	mean.ta	mean.rh	total.radiation.umol.m2.s	CO2.ppm	mean.wind.speed.m.s	swp.MPa	year	stn.no.

```{r,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# relative humidity data are mainly missing from the data
blenheim.radiation <- 
  tbl_df(read.csv(file.path(IntermediateResults, 
                            'MRL.climate.data.hourly.csv'), header = TRUE)) %>% 
  select(year, day, hour, total.radiation.umol.m2.s,CO2.ppm,swp.MPa  )
   

glimpse(blenheim.radiation)

complete.radiation <-
  left_join(hourly.data.new, blenheim.radiation, by = c('year','day', 'hour')) %>% 
  group_by(year,day, hour) %>% 
  mutate_at('total.radiation.umol.m2.s',funs(replace(.,is.na(.), mean(.,na.rm=TRUE)))) %>% 
  mutate_at('CO2.ppm', funs(replace(.,is.na(.), mean(.,na.rm=TRUE)))) %>% 
   mutate_at('swp.MPa', funs(replace(.,is.na(.), mean(.,na.rm=TRUE))))  


short_summary(complete.radiation)  

```
#organize the data for input into GroIMP 
```{r, fig.width=15, fig.height=25,echo=FALSE}
FPAR = 0.55
WATT_TO_PPFD = 4.55
    
date = as.Date("2019-2-04")
yday(date)
leap_year(2019)
  
climate.data.hourly <- 
  complete.radiation %>% 
  
  mutate(stn.no. = 93) %>%
   mutate(CO2.ppm = 400, swp.MPa = -0.2, mean.rh = mean.rh/100 ) %>% 
     select(day, hour, mean.ta, mean.rh,total.radiation.umol.m2.s,CO2.ppm, mean.wind.speed.m.s, swp.MPa, year, stn.no.) #%>%
  #filter((year == 2019))

tail(climate.data.hourly)
    
write_csv(climate.data.hourly, file.path(IntermediateResults, 
                    paste('RPC.climate.data.hourly.csv',sep = '')))        
names(climate.data.hourly)
range(climate.data.hourly$mean.ta)
  
```